Selective electroporation of the viral envelope

### 2021-04-11 documents/EPA_paper.tex
w

I can find no reference to such a conference in Annals of the NYAS, but it may be recorded in Transactions. It is a shame to see good work fade into the mist of time, especially since research in this field attained an acceptable level of quality even in the 1940s. O. N. Fellowes was of the Plum Island Animal Disease Laboratory. Oscar S. Gray was of Gray Industries Inc, Florida.

>>>>

I can find no reference to such a conference in Annals of the NYAS, but it may be recorded in Transactions. It is a shame to see any work fade into the mist of time, especially since research in this field attained an acceptable level of quality even in the 1940s. O. N. Fellowes was of the Plum Island Animal Disease Laboratory. Oscar S. Gray was of Gray Industries Inc, Florida.
